Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-01-07 tex/test-WW-type-00s-PS.tex
alexei

In the Gauss Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
has the form
\begin{subequations}\ba
	F_{LT}^{\cos(\phi_h -\phi_S)}(x,z,\Phperp) 
	&=& x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \\
	F_{LT}^{\cos(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=&  x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
	\label{eq:asymmetry_g1t_pt-II}
\ea\end{subequations}
where 
$\lambda  = z^2 \avkperp_{g_{1T}^\perp} + \avpperp_{D_1}$,
$b^{(1)}_{\rm B} = 2M_N$,
$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$,
see App.~\ref{App:convol-details} for details.
We remind that $g^{\perp q}_{1T}$ and the Sivers function are both 
constrained by the positivity bound \cite{Bacchetta:1999kz} 
\be
	\frac{\kperp^2}{M^2}\left( (g^{\perp q}_{1T}(x,\kperp^2))^2 
	+ (f_{1T}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 
\ee
so that one has
\be
\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(f_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{f_{1T}^\perp} } -
\frac{(g_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{g_{1T}^\perp} } \ge 0
\label{eq:positivity}
\ee
see Fig.~\ref{g1t_pos}.

@@

We assume Gaussian form for Kotzinian-Mulders function $h_{1L}^{\perp a}$:
\be
	h_{1L}^{\perp a}(x,\kperp^2) = h_{1L}^{\perp (1) a}(x)\,
	\frac{2 M^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
	\;,\label{eq:h1l_final}
\ee
We will use WW-type approximation from Eq.~(\ref{Eq:WW-approx-h1L}) 
for calculation of $h_{1L}^{\perp (1) a}(x)$ and for the estimates of the 
asymmetry $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}} = 0.25$ (GeV$^2$).
Notice that the Kotzinian-Mulders function and $h^{\perp q}_{1L}$ obey the
positivity bound \cite{Bacchetta:1999kz}
\be
	\frac{\kperp^2}{M^2}\left( (h^{\perp q}_{1L}(x,\kperp^2))^2 + 
	(h_{1}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 \, .
\ee
so that one has
\be
\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(h_{1}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1}^\perp} } -
\frac{(h_{1L}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1TL}^\perp} } \ge 0
\label{eq:positivity1}
\ee
which is plottde in Fig.~\ref{h1l_pos}. Notice that for $d$-quark the positivity is violated that may be due to the big Boer-Mulders $d$-quark function from Ref.~\cite{Barone:2015ksa}. As far as determination of the size of Boer-Mulders functions is far from ideal, we cautiously keep the present result. Future determinations of Boer-Mulders functions will help to clarify the issue of positivity constraints.

@@

In the WW-type approximation the structure function
$F_{LT}^{\cos\phi_S}$ is due to $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
whose collinear counterparts are more or less well known, see
Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
Assuming the Gaussian Ansatz for $g_T^a(x,\kperp)$ yields for the
structure function 
\begin{subequations}\ba
	F_{LT}^{\cos\phi_S}(x,z,\Phperp) 
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\,g_T^q(x)\,D_1^q(z)\;   
	{ \cal G}(\Phperp)\, , \label{Eq:FLTcosphiS-Gauss}\\
	F_{LT}^{\cos\phi_S}(x,z)
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\, g_T^q(x)\,D_1^q(z)\, ,
\ea\end{subequations}
{\color{blue} AP - I disagree with \ref{Eq:FLTcosphiS-Gauss} see my notes}
with the width $\lambda= z^2 \avkperp_{g_T} + \avpperp_{D_1}$
in the Gaussian ${\cal G}(\Phperp)$. We estimate $g_T^a(x)$ in terms 
of $g_1^a(x)$ according to Eq.~(\ref{Eq:WW-original1}) assuming for 
the Gaussian width $\avkperp_{g_T}=\avkperp_{g_1}$.\footnote{
	Notice that one could also proceed in a different way: 
	explore first the WW-type-relation (\ref{Eq:WW-type-5}), and
	assume then the Gauss Ansatz for $g_{1T}^{\perp}(x,\kperp)$ 
	according to (\ref{eq:g1t}). Solving then the convolution integral 
	yields a result different from (\ref{Eq:FLTcosphiS-Gauss})
	which depends much more strongly on Gaussian model parameters.
	The operations of applying the WW-type approximations and 
	employing the Gauss Ansatz do not commute in general.
	The solution presented in (\ref{Eq:FLTcosphiS-Gauss}) is 
	preferable as it helps to minimize model dependence.}

Asymmetries $A_{LT}^{\cos\phi_S} = F_{LT}^{\cos\phi_S}/F_{UU}$ for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{altcosphi_jlab}.
Notice that the asymmetry scales at small transverse hadron
momenta as $A_{LT}^{\cos\phi_S} \propto (\Phperp)^0$ which makes
it easier to measure if longitudinally polarized lepton beams
and transversely polarized targets are available.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_PT.pdf}
\caption{\label{altcosphi_jlab} $A_{LT}^{\cos\phi_S}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In the Gauss Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
has the form
\begin{subequations}\ba
	F_{LT}^{\cos(\phi_h -\phi_S)}(x,z,\Phperp) 
	&=& x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \\
	F_{LT}^{\cos(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=&  x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
	\label{eq:asymmetry_g1t_pt-II}
\ea\end{subequations}
where 
$\lambda  = z^2 \avkperp_{g_{1T}^\perp} + \avpperp_{D_1}$,
$b^{(1)}_{\rm B} = 2M_N$,
$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$,
see App.~\ref{App:convol-details} for details.
The $g^{\perp q}_{1T}$ and the Sivers function $f^{\perp q}_{1T}$ are both 
constrained by the positivity bound \cite{Bacchetta:1999kz} 
\be
	\frac{\kperp^2}{M^2}\left( (g^{\perp q}_{1T}(x,\kperp^2))^2 
	+ (f_{1T}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 
\ee
so that using our Gaussian parametrizations from Eqs.~(\ref{Eq:Gauss-f1-D1},\ref{eq:g1t},\ref{sivers_new}) one has
\be
\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(f_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{f_{1T}^\perp} } -
\frac{(g_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{g_{1T}^\perp} } \ge 0
\label{eq:positivity}
\ee
see Fig.~\ref{g1t_pos} where RHS of this equation multiplied by $16\pi M^2$ is shown.

@@

We assume Gaussian form for Kotzinian-Mulders function $h_{1L}^{\perp a}$:
\be
	h_{1L}^{\perp a}(x,\kperp^2) = h_{1L}^{\perp (1) a}(x)\,
	\frac{2 M^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
	\;,\label{eq:h1l_final}
\ee
We will use WW-type approximation from Eq.~(\ref{Eq:WW-approx-h1L}) 
for calculation of $h_{1L}^{\perp (1) a}(x)$ and for the estimates of the 
asymmetry $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}} = 0.25$ (GeV$^2$).
Notice that the Kotzinian-Mulders function and $h^{\perp q}_{1L}$ obey the
positivity bound \cite{Bacchetta:1999kz}
\be
	\frac{\kperp^2}{M^2}\left( (h^{\perp q}_{1L}(x,\kperp^2))^2 + 
	(h_{1}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 \, .
\ee
so that using our Gaussian parametrizations from Eqs.~(\ref{Eq:Gauss-f1-D1},\ref{eq:h1l_final},\ref{bm_new})  one has
\be
\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(h_{1}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1}^\perp} } -
\frac{(h_{1L}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1TL}^\perp} } \ge 0
\label{eq:positivity1}
\ee
which, multiplied by $16\pi M^2$,  is plotted in Fig.~\ref{h1l_pos}. Notice that for $d$-quark the positivity is violated that may be due to the big Boer-Mulders $d$-quark function from Ref.~\cite{Barone:2015ksa}. As far as determination of the size of Boer-Mulders functions is far from ideal, we cautiously keep the present result. Future determinations of Boer-Mulders functions will help to clarify the issue of positivity constraints.

@@

In the WW-type approximation the structure function
$F_{LT}^{\cos\phi_S}$ is due to $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
whose collinear counterparts are more or less well known, see
Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.

We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$ 
\be
	g^{q}_{T}(x,\kperp^2) = 
	g^{q}_{T}(x)\,\frac{1}{\pi \avkperp_{g_{T}}}\,
	e^{-\kperp^2/{\avkperp_{g_{T}}}}\;,
	\label{eq:gtnew}
\ee
where $g^{q}_{T}(x)$ is calculated according to Eq.~\ref{Eq:WW-original1}.
Notice that we could have used WW-type relation of Eq.~(\ref{Eq:WW-type-6}) to relate $g^{q}_{T}(x,\kperp^2)$
and $g^{\perp q}_{1T}(x,\kperp^2)$ however we choose not to do it. In fact Eq.~(\ref{Eq:WW-type-6}) suggests kinematical zero 
$g^{q}_{T}(x, 0) = 0$  which is not supported by the model calculations \cite{Avakian:2010br} and thus  Eq.~(\ref{Eq:WW-type-6}) can be used only in its integrated form. 
The Eq.~(\ref{Eq:WW-type-6}) is not exact and is not on the same footing as WW-approximation of Eq.~(\ref{Eq:WW-original1}), and we parametrize directly $g^{q}_{T}(x,\kperp^2)$ using the Gaussian shape. For illustrative purpose we show ``violation'' of  Eq.~(\ref{Eq:WW-type-6}) in Fig.~\ref{altcosphi_wwtype}.

$F_{LT}^{\cos\phi_S}$
structure function then reads 
\begin{subequations}\ba
	F_{LT}^{\cos\phi_S}(x,z,\Phperp) 
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\,g_T^q(x)\,D_1^q(z)\;   
	{ \cal G}(\Phperp)\, , \label{Eq:FLTcosphiS-Gauss}\\
	F_{LT}^{\cos\phi_S}(x,z)
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\, g_T^q(x)\,D_1^q(z)\, ,
\ea\end{subequations}
with the width $\lambda= z^2 \avkperp_{g_T} + \avpperp_{D_1}$
in the Gaussian ${\cal G}(\Phperp)$. We estimate $g_T^a(x)$ in terms 
of $g_1^a(x)$ according to Eq.~(\ref{Eq:WW-original1}) assuming for 
the Gaussian width $\avkperp_{g_T}=\avkperp_{g_1}$.\footnote{
	Notice that one could also proceed in a different way: 
	explore first the WW-type-relation (\ref{Eq:WW-type-5}), and
	assume then the Gauss Ansatz for $g_{1T}^{\perp}(x,\kperp)$ 
	according to (\ref{eq:g1t}). Solving then the convolution integral 
	yields a result different from (\ref{Eq:FLTcosphiS-Gauss})
	which depends much more strongly on Gaussian model parameters.
	The operations of applying the WW-type approximations and 
	employing the Gauss Ansatz do not commute in general.
	The solution presented in (\ref{Eq:FLTcosphiS-Gauss}) is 
	preferable as it helps to minimize model dependence.}

Asymmetries $A_{LT}^{\cos\phi_S} = F_{LT}^{\cos\phi_S}/F_{UU}$ for 
COMPASS are plotted in Fig.~\ref{altcosphi_jlab}.
Notice that the asymmetry scales at small transverse hadron
momenta as $A_{LT}^{\cos\phi_S} \propto (\Phperp)^0$ which makes
it easier to measure if longitudinally polarized lepton beams
and transversely polarized targets are available.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_COMPASS_x.pdf} 
\caption{\label{altcosphi_jlab} $A_{LT}^{\cos\phi_S}$  as a function of $ x $.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 %%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/gT_vs_g1Tperp_wwtype.pdf} 
\caption{\label{altcosphi_wwtype} RHS and LHS of Eq.~\ref{Eq:WW-type-6}.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
